Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
revised more of reddening discussion

To achieve this empirical calibration, we must adopt a set of ``calibrators''
for which true reddening is known. There are various possibilities
at our disposal. SFD used XX. \cite{planckdust} used quasars. Here we use
the SSPP stars with SDSS spectra and photometry studied by \cite{schlafly10}.

>>>>

To achieve this empirical calibration, we must adopt a set of calibrator
objects for which true optical reddening is known. There are various 
possibilities at our disposal. \cite{planckdust} calibrated their single MBB
$\tau_{353}$ to $E(B-V)$ using broadband SDSS photometry for a set of 
$\sim$10$^5$ quasars. The SFD calibration was originally tied to a few
hundred elliptical galaxies, but was later revised by \cite{schlafly10} using 
several hundred thousand stars with both spectroscopy and broadband photometry 
available from SDSS. To calibrate our $\tau_{545}$ to reddening, we make use of
the same set of stars studied by \cite{schlafly10}.

% do I need to cite a reference the first time that i mention SDSS ?

% maybe note the possibility in the future of calibrating to a 3D dust
% map type data product rather than directly to a set of individual 
% stars/galaxies
